\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2016-07-17 doc/USER_MANUAL/04_creating_databases.tex
Buildbot ran the code beautifier.
added a sentence about free surfaces versus rigid surfaces
clarified a couple of print statements about attenuation, and updated the users manual accordingly

@@

>>>>

The code uses a constant $Q$ quality factor, write(IMAIN,*) "but approximated based on a series of Zener standard linear solids (SLS).
The approximation is thus performed in a given frequency band determined based on that \texttt{ATTENUATION\_f0\_REFERENCE} reference frequency.

@@

\item [{\texttt{BOTTOM\_FREE\_SURFACE}}]
When STACEY\_ABSORBING\_CONDITIONS is set to .true. :
absorbing conditions are defined in xmin, xmax, ymin, ymax and zmin
this option BOTTOM\_FREE\_SURFACE can be set to .true. to
make zmin free surface instead of absorbing condition.
